### 2022-10-13 types.tex
general notes on weakening

>>>>

\section{general notes}

Something we originally wanted to do was relaxations---operators that happened to consume input $'s$, but could just as well accept any $"permute"('s)$.  How do we want to model this relaxation now, and is it still in scope? Concretely, I believe that this _is_ still in scope, and takes the form of setting translation-preservation targets to literal expressions like $"permute"('s)$.  The challenge here will be reasoning in the algebra; we're not talking about equational rewriting anymore, since we also need to include weakening ("permute" generalizes lots of transformations).
